\documentclass{beamer}
\usebeamertemplate{default}
\begin{document}
\begin{frame}
\begin{center}
\Huge{PROJECT PROPOSAL}\\[20pt]
\large{MODEL ENGINEERING COLLEGE ERNAKULAM\\[5pt]Department of Computer Science and Engineering}\\[5pt]
\large{\color{blue}PLACEMENT CELL MANAGEMENT SYSTEM}\\[6pt]
17th January 2017
\end{center}
\begin{flushright}
\large{GROUP 4\\AJAY JOHN(3)\\AMEL JOHNY(12)\\ANJANA MUKESH(15)\\S MEENA PADNEKAR(47)}
\end{flushright}
\end{frame}
\begin{frame}
\begin{flushleft}
\Large{\textbf{PROJECT DOMAIN}}\\[20pt]
\textbf{*} Online web application for automation of Placement activities. \\
\textbf{*}Organized database for easy and flexible retrieval of desired data.  
\end{flushleft}
\end{frame}
\begin{frame}
\begin{flushleft}
\Large{\textbf{EXISTING SYSTEM}} \\[20pt]
\normalsize{\textbf{*}In various colleges, training and placement officers have to manage the students’ profile and associated documents manually.}\\
\normalsize{\textbf{*}Information about various companies who want to recruit students has to be collected and also notify students time to time about them.}\\
\normalsize{\textbf{*}If any modifications or updates are required in the profile of any student, it has to be searched and to be done manually which is tedious and time consuming. This process is so difficult when number of users increases.}\\
\normalsize{\textbf{*}Lack of security of data, more man power, consumption of large volume of paper and space are other drawbacks of the existing system.}
\end{flushleft}
\end{frame}
\begin{frame}
\begin{flushleft}
\Large{\textbf{PROBLEM STATEMENT} }\\[20pt]
\normalsize{This project is aimed at developing an online application for the Placement Department of the College that can be accessed throughout the organisation with proper login provided. This system provides automation, integration and proper communication channel}
\end{flushleft}
\end{frame}
\begin{frame}
\begin{flushleft}
\Large{\textbf{PROPOSED SYSTEM} }\\[20pt]
\normalsize{\textbf{*}Our application integrates all the required services at one place}\\
\normalsize{\textbf{*}Students’ information is maintained in a database which provides more security to data, ensures data accuracy and reduces paperwork }\\
\normalsize{\textbf{*}It makes information flow efficient and paves way for easy report generation and reduces time.}\\
\normalsize{\textbf{*}Proposed system is also cost effective.}\\
\normalsize{\textbf{*}It provides a better communication using appropriate notification}
\end{flushleft}
\end{frame}
\begin{frame}
\begin{flushleft}
\Large{\textbf{HARDWARE AND SOFTWARE REQUIREMENTS}}\\[20pt]
\large{HARDWARE}\\[10pt]
	Processor Intel Pentium Dual Core or above\\
	Minimum 64GB harddisk\\
	Minimum 2GB RAM\\[20pt]
\large{SOFTWARE}\\[10pt]
Django\\SQLite3, Python\\HTML, CSS, Javascript, PHP	
\end{flushleft}
\end{frame}
\begin{frame}
\begin{flushleft}
\Large{\textbf{SCHEDULE}} \\[40pt]
\begin{center}
 \small{\begin{tabular}{||c c  c ||} 
 \hline
 WEEK & WORK & DURATION   \\ [0.5ex] 
 \hline\hline
 Week1 & ProjectDesign & 18/1-23/1 \\
 \hline
 Week2 & Home page and Student view&24/1-30/1 \\
 \hline
 Week3 & PC member view  &31/1-6/2   \\
 \hline
 Week4 & Database manipulation (phase1) &7/2-13/2   \\
 \hline
  Week5 & Database Manipulation(phase2) & 14/2-20/2   \\
  \hline
   Week6 & Features for communication(phase1) &21/2-27/2   \\
   \hline
    Week7 & Features for communication(phase2) & 28/2-6/3   \\
    \hline
 Week8 & software testing &7/3-14/3   \\ [1ex] 
 \hline
\end{tabular}}
\end{center}

\end{flushleft}
\end{frame}
\end{document}